---
title: "R-Club-Aug-9"
author: "Hajar"
date: "8/8/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "R-Club"
author: "Hajar"
date: "8/4/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#15 Factors
```{r}
library(tidyverse)
library(forcats)
```

#15.2 Creating factors

```{r}
x1 <- c("Dec", "Apr", "Jan", "Mar")
sort(x1)
month_levels <- c(
  "Jan", "Feb", "Mar", "Apr", "May", "Jun", 
  "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"
)
y1 <- factor (x1, levels = month_levels)
sort(y1)
y1 <- factor(x1)

f1 <- factor(x1, levels = unique(x1))
f1
f2 <- x1 %>% factor() %>% fct_inorder()
f2

```

#15.3 General Social Survey

```{r}
gss_cat
gss_cat %>% 
  count (race)

ggplot(gss_cat, aes(race)) +
  geom_bar()

ggplot(gss_cat, aes(race)) +
  geom_bar() +
  scale_x_discrete(drop = FALSE)

```

#15.3.1 Exercise

1.Explore the distribution of rincome (reported income). What makes the default bar chart hard to understand? How could you improve the plot?

```{r}
rincome_plot <-
  gss_cat %>%
  ggplot(aes(rincome)) +
  geom_bar()

rincome_plot

#The default bar chart labels are too mix to read. One solution is to change the angle of the labels.

rincome_plot +
  theme(axis.text.x = element_text(angle = 90))

#make it better with change the x with y axis
rincome_plot +
  coord_flip()

```

2.What is the most common relig in this survey? What’s the most common partyid?

```{r}
gss_cat %>%
  count(relig)
  arrange(-n) %>%
  head(1)
  

#The most common relig is Protestant

  gss_cat %>%
  count(partyid) %>% 
  arrange(-n) %>%
  head(1)
```

3.Which relig does denom (denomination) apply to? How can you find out with a table? How can you find out with a visualisation?

```{r}
levels(gss_cat$denom)

#filter out the non-responses, no answers, others, not-applicable, or no denomination, to leave only answers to denominations. 

gss_cat %>%
  filter(!denom %in% c("No answer", "Other", "Don't know", "Not applicable",
                       "No denomination")) %>%
  count(relig)

gss_cat %>%
  count(relig, denom) %>%
  ggplot(aes(x = relig, y = denom, size = n)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90))

```

#16 Dates and times

#16.1.1 Prerequisites

```{r}
library(tidyverse)

library(lubridate)
library(nycflights13)

```

```{r}
today()
now()
```

#16.2.1 From strings

```
ymd("2017-01-31")
mdy("January 31st, 2017")
dmy("31-Jan-2017")
ymd(20170131)
ymd_hms("2017-01-31 20:11:59")
mdy_hm("01/31/2017 08:01")
ymd(20170131, tz = "UTC")

```

#16.2.2 From individual components

```{r}
flights %>% 
  select(year, month, day, hour, minute)

flights %>% 
  select(year, month, day, hour, minute) %>% 
  mutate(departure = make_datetime(year, month, day, hour, minute))

make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights_dt <- flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time)) %>% 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime_100(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime_100(year, month, day, sched_arr_time)
  ) %>% 
  select(origin, dest, ends_with("delay"), ends_with("time"))

flights_dt

```

#16.2.3 From other types

```{r}

as_datetime(today())

as_date(now())

```

#16.2.4 Exercises

1.What happens if you parse a string that contains invalid dates?

```{r}
#ymd(c("2010-10-10", "bananas"))
#error and warning

2.What does the tzone argument to today() do? Why is it important?

#It determines the time-zone of the date. Since different time-zones can have different dates, the value of today() can vary depending on the time-zone specified.

3.Use the appropriate lubridate function to parse each of the following dates:

d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" 
```

#16.3 Date-time components

```{r}

datetime <- ymd_hms("2016-07-08 12:34:56")

year(datetime)
month(datetime)
mday(datetime)

yday(datetime)

wday(datetime)

month(datetime, label = TRUE)

wday(datetime, label = TRUE, abbr = FALSE)

```

#16.3.4 Exercises

1.How does the distribution of flight times within a day change over the course of the year?

```{r}

flights_dt %>%
  mutate(time = hour(dep_time) * 100 + minute(dep_time),
         mon = as.factor(month
                         (dep_time))) %>%
  ggplot(aes(x = time, group = mon, color = mon)) +
  geom_freqpoly(binwidth = 100)

Compare dep_time, sched_dep_time and dep_delay. Are they consistent? Explain your findings.

Compare air_time with the duration between the departure and arrival. Explain your findings. (Hint: consider the location of the airport.)

How does the average delay time change over the course of a day? Should you use dep_time or sched_dep_time? Why?

On what day of the week should you leave if you want to minimise the chance of a delay?

What makes the distribution of diamonds$carat and flights$sched_dep_time similar?

Confirm my hypothesis that the early departures of flights in minutes 20-30 and 50-60 are caused by scheduled flights that leave early. Hint: create a binary variable that tells you whether or not a flight was delayed

```

#18 Pipes

18.1 Introduction

```{r}
library(magrittr)

```

#18.2 Piping alternatives

```{r}

library(pryr)
diamonds <- ggplot2::diamonds
diamonds2 <- diamonds %>% 
  dplyr::mutate(price_per_carat = price / carat)

pryr::object_size(diamonds) #3.49MB

pryr::object_size(diamonds2) #3.89MB

pryr::object_size(diamonds, diamonds2) #3.89

diamonds$carat[1] <- NA
pryr::object_size(diamonds) 
#> 3.46 MB
pryr::object_size(diamonds2)
#> 3.89 MB
pryr::object_size(diamonds, diamonds2)
#> 4.32 MB

assign("x", 10)
x
#> [1] 10

"x" %>% assign(100)
x

env <- environment()
"x" %>% assign(100, envir = env)
x
?tryCatch
tryCatch(stop("!"), error = function(e) "An error")
stop("!") %>% 
  tryCatch(error = function(e) "An error")
?try
?suppressMessages
?suppressWarnings

rnorm(100) %>%
  matrix(ncol = 2) %>%
  plot() %>%
  str()

rnorm(100) %>%
  matrix(ncol = 2) %T>%
  plot() %>%
  str()

mtcars %$%
  cor(disp, mpg)

mtcars <- mtcars %>% 
  transform(cyl = cyl * 2)

mtcars %<>% transform(cyl = cyl * 2)
