---
title: "R-club-May-31"
author: "Hajar"
date: "May 29, 2017"
output: 
  html_document: 
    keep_md: yes
---

#7.6 Patterns and models

```{r}
library(ggplot2)
ggplot(data = faithful) + 
  geom_point(mapping = aes(x = eruptions, y = waiting))

```

```{r}
library(modelr)
library(dplyr)
mod <- lm(log(price) ~ log(carat), data = diamonds)


diamonds2 <- diamonds %>% 
  add_residuals(mod) %>% 
  mutate(resid = exp(resid))

ggplot(data = diamonds2) + 
  geom_point(mapping = aes(x = carat, y = resid))

```

```{r}
ggplot(data = diamonds2) + 
  geom_boxplot(mapping = aes(x = cut, y = resid))

```

#7.7 ggplot2 calls

```{r}

ggplot(data = faithful, mapping = aes(x = eruptions)) + 
  geom_freqpoly(binwidth = 0.25)

ggplot(faithful, aes(eruptions)) + 
  geom_freqpoly(binwidth = 0.25)

diamonds %>% 
  count(cut, clarity) %>% 
  ggplot(aes(clarity, cut, fill = n)) + 
    geom_tile()

```
#7.8 Learning more

#10 Tibbles

#10.1.1 Prerequisites

```{r}
library(tidyverse)
```

#10.2 Creating tibbles

```{r}
as_tibble(iris)

tibble(
  x = 1:5, 
  y = 1, 
  z = x ^ 2 + y
)

tb <- tibble(
  `:)` = "smile", 
  ` ` = "space",
  `2000` = "number"
)
tb

```

#10.3 Tibbles vs. data.frame
#10.3.1 Printing

```{r}
tibble(
  a = lubridate::now() + runif(1e3) * 86400,
  b = lubridate::today() + runif(1e3) * 30,
  c = 1:1e3,
  d = runif(1e3),
  e = sample(letters, 1e3, replace = TRUE)
)

nycflights13::flights %>% 
  print(n = 10, width = Inf)

nycflights13::flights %>% 
  View()
```

#10.3.2 Subsetting

```{r}
df <- tibble(
  x = runif(5),
  y = rnorm(5)
)
df$x
df[["x"]]
df[[1]]

df %>% .$x
df %>% .[["x"]]

```

#0.4 Interacting with older code

```{r}
class(tb)
str(tb)
class(as.data.frame(tb))

```

#10.5 Exercises

1.How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

```{r}
print(mtcars)
str(mtcars)
class(mtcars)

```

2.Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r}
#on a dataframe
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

```

```{r}
# on a tibble
df <- tibble(abc = 1, xyz = "a")
df$x
#> Warning: Unknown column 'x'
#> NULL
df[, "xyz"]
df[, c("abc", "xyz")]

#Tibbles never do partial matching; data frames do.

```

3.If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
var <- "hwy"
mpg[[var]]

# i am not sure
```

4.Practice referring to non-syntactic names in the following data frame by:

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

#1.Extracting the variable called 1.
annoying$`1`

#2.Plotting a scatterplot of 1 vs 2.

ggplot(annoying, aes(`1`, `2`)) +
  geom_point()

#3.Creating a new column called 3 which is 2 divided by 1.

annoying <- mutate(annoying, `3` = `2` / `1`)
annoying

#4.Renaming the columns to one, two and three.

rename(annoying,
       one = `1`,
       two = `2`,
       three = `3`)

```

#5.What does tibble::enframe() do? When might you use it?

```{r}
?enframe
enframe(c(a = 5, b = 7))
enframe(1:6)

#enframe() is a function that converts named atomic vectors or lists to two-column data frames. we use it if we have data stored in a named vector and we want to add it to a data frame and preserve both the name attribute and the actual value.

```

#6.What option controls how many additional column names are printed at the footer of a tibble?

```{r}
?print.tbl_df

nycflights13::flights %>% 
  print(n = 4, width = Inf) 
# n for rows, width = Inf means print all columns  

nycflights13::flights %>% 
  print(n = 4, width = NULL, n_extra = 3)  

```

