---
title: "R-club-28-Jun"
author: "Hajar"
date: "6/28/2017"
output: 
  html_document: 
    keep_md: yes
---
#13.3 Keys
```{r}
library(tidyverse)
library(nycflights13)
planes %>% 
  count(tailnum) %>% 
  filter(n > 1)

weather %>% 
  count(year, month, day, hour, origin) %>% 
  filter(n > 1)
```

#13.3.1 Exercises
1.Add a surrogate key to flights.
I add the column flight_id as a surrogate key.
```{r}
flights %>% 
  arrange(year, month, day, dep_time, carrier, flight) %>%
  mutate(flight_id = row_number()) %>%
  glimpse()
```

2.Identify the keys in the following datasets

Lahman::Batting,
babynames::babynames
nasaweather::atmos
fueleconomy::vehicles
ggplot2::diamonds

```{r}
#The primary key for Lahman::Batting is playerID, yearID, stint
Lahman::Batting %>%
  group_by(playerID, yearID, stint) %>%
  filter(n() > 1) %>%
  nrow()

#install.packages("babynames")
library(babynames)
babynames::babynames %>%
  group_by(year, sex, name) %>%
  filter(n() > 1) %>%
  nrow()
#install.packages("nasaweather")
nasaweather::atmos %>%
  group_by(lat, long, year, month) %>%
  filter(n() > 1) %>%
  nrow()

#install.packages("fueleconomy")
fueleconomy::vehicles %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  nrow()

#here is no primary key for ggplot2::diamonds. Using all variables in the data frame,
#the number of distinct rows is lower than the total number of rows.(no combination of variabl)

ggplot2::diamonds %>%
  distinct() %>% 
  nrow()

nrow(ggplot2::diamonds)
```
3.Draw a diagram illustrating the connections between the Batting, Master, and Salaries tables in the Lahman package. Draw another diagram that shows the relationship between Master, Managers, AwardsManagers.

How would you characterise the relationship between the Batting, Pitching, and Fielding tables?

-Batting
primary key: playerID, yearID, stint
foreign keys:
  playerID -> Master.playerID
-Master
primary key: playerID
-Salaries
primary key: yearID, teamID, playerID
foreign keys:
  playerID -> Master.playerID
-Managers:
  primary key: yearID, playerID, teamID, inseason
foreign keys:
  playerID -> Master.teamID
Managers:
  primary key: awardID, yearID
-AwardsManagers:
  primary key: playerID, awardID, yearID (since there are ties and while tie distinguishes those awards it has NA values)
foreign keys:
  playerID -> Master.playerID
playerID, yearID, lgID -> Managers.playerID, yearID, lgID

#13.4 Mutating joins
```{r}
flights2 <- flights %>% 
  select(year:day, hour, origin, dest, tailnum, carrier)
flights2

#flights2 %>%
  #select(-origin, -dest) %>% 
  #left_join(airlines, by = "carrier")

flights2 %>%
  select(-origin, -dest) %>% 
  mutate(name = airlines$name[match(carrier, airlines$carrier)])
```
#13.4.1 Understanding joins
```{r}
x <- tribble(
  ~key, ~val_x,
  1, "x1",
  2, "x2",
  3, "x3"
)
y <- tribble(
  ~key, ~val_y,
  1, "y1",
  2, "y2",
  4, "y3"
)
```
#13.4.2 Inner join
```{r}
x %>% 
  inner_join(y, by = "key")
```
#13.4.3 Outer joins
#13.4.4 Duplicate keys
```{r}
x <- tribble(
  ~key, ~val_x,
  1, "x1",
  2, "x2",
  2, "x3",
  1, "x4"
)

y <- tribble(
  ~key, ~val_y,
  1, "y1",
  2, "y2"
)
left_join(x, y, by = "key")
```

```{r}
x <- tribble(
  ~key, ~val_x,
  1, "x1",
  2, "x2",
  2, "x3",
  3, "x4"
)
y <- tribble(
  ~key, ~val_y,
  1, "y1",
  2, "y2",
  2, "y3",
  3, "y4"
)
left_join(x, y, by = "key")
```
#13.4.5 Defining the key columns
```{r}
flights2 %>% 
  left_join(weather)

flights2 %>% 
  left_join(airports, c("dest" = "faa"))
```

#13.4.6 Exercises

1.Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States:

```{r}
airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```

```{r}
avg_dest_delays <-
  flights %>%
  group_by(dest) %>%
  # arrival delay NA's are cancelled flights
  summarise(delay = mean(arr_delay, na.rm = TRUE)) %>%
  inner_join(airports, by = c(dest = "faa"))

avg_dest_delays %>%
  ggplot(aes(lon, lat, colour = delay)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```

2.Add the location of the origin and destination (i.e. the lat and lon) to flights.

```{r}
flights %>%
  left_join(airports, by = c(dest = "faa")) %>%
  left_join(airports, by = c(origin = "faa")) %>%
  head()
```
3.Is there a relationship between the age of a plane and its delays?
I don't think so

```{r}
plane_ages <- 
  planes %>%
  mutate(age = 2013 - year) %>%
  select(tailnum, age)

flights %>%
  inner_join(plane_ages, by = "tailnum") %>%
  group_by(age) %>%
  filter(!is.na(dep_delay)) %>%
  summarise(delay = mean(dep_delay)) %>%
  ggplot(aes(x = age, y = delay)) +
  geom_point() +
  geom_line()
```
4.What weather conditions make it more likely to see a delay?
Almost any precipitation is associated with a delay, though not as strong a trend after 0.02

```{r}
flight_weather <-
  flights %>%
  inner_join(weather, by = c("origin" = "origin",
                            "year" = "year",
                            "month" = "month",
                            "day" = "day",
                            "hour" = "hour"))

flight_weather %>%
  group_by(precip) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = precip, y = delay)) +
    geom_line() + geom_point()
```
5.What happened on June 13 2013? Display the spatial pattern of delays, and then use Google to cross-reference with the weather.
There was a large series of storms in the southeastern US (see June 12-13, 2013 derecho series)
The largest delays are in Tennessee (Nashville) and the Southeaste and Midwest (the location of the derechos).

```{r}
#install.packages("viridis")
library(viridis)
flights %>%
  filter(year == 2013, month == 6, day == 13) %>%
  group_by(dest) %>%
  summarise(delay = mean(arr_delay, na.rm = TRUE)) %>%
  inner_join(airports, by = c("dest" = "faa")) %>%
  ggplot(aes(y = lat, x = lon, size = delay, colour = delay)) +
  borders("state") +
  geom_point() +
  coord_quickmap() + 
  scale_color_viridis()
```
#13.4.7 Other implementations
#13.5 Filtering joins

```{r}
top_dest <- flights %>%
  count(dest, sort = TRUE) %>%
  head(10)
top_dest

flights %>% 
  filter(dest %in% top_dest$dest)


```
#3.5.1 Exercises

1.What does it mean for a flight to have a missing tailnum? What do the tail numbers that don’t have a matching record in planes have in common? (Hint: one variable explains ~90% of the problems.)
American Airlines (AA) and Envoy Airlines (MQ) don’t report tail numbers.

```{r}
flights %>%
  anti_join(planes, by = "tailnum") %>%
  count(carrier, sort = TRUE)
```


2.Filter flights to only show flights with planes that have flown at least 100 flights.

```{r}
planes_gt100 <- 
  filter(flights) %>%
  group_by(tailnum) %>%
  count() %>%
  filter(n > 100)

flights %>%
  semi_join(planes_gt100, by = "tailnum")
```


3.Combine fueleconomy::vehicles and fueleconomy::common to find only the records for the most common models.

```{r}
glimpse(fueleconomy::vehicles)

glimpse(fueleconomy::common)

fueleconomy::vehicles %>%
  semi_join(fueleconomy::common, by = c("make", "model"))
```


4.Find the 48 hours (over the course of the whole year) that have the worst delays. Cross-reference it with the weather data. Can you see any patterns?

5.What does anti_join(flights, airports, by = c("dest" = "faa")) tell you? What does anti_join(airports, flights, by = c("faa" = "dest")) tell you?

anti_join(flights, airports, by = c("dest" = "faa")) are flights that go to an airport that is not in FAA list of destinations, likely foreign airports.

anti_join(airports, flights, by = c("faa" = "dest")) are US airports that don’t have a flight in the data, meaning that there were no flights to that aiport from New York in 2013.

6.You might expect that there’s an implicit relationship between plane and airline, because each plane is flown by a single airline. Confirm or reject this hypothesis using the tools you’ve learned above.

```{r}
flights %>%
  group_by(tailnum, carrier) %>%
  count() %>%
  filter(n() > 1) %>%
  select(tailnum) %>%
  distinct()
```

