---
title: "R-club-May-17"
author: "Hajar"
date: "May 13, 2017"
output: 
  html_document: 
    keep_md: yes
---
#5.6 Grouped summaries with summarise()

```{r}
library(nycflights13)
library(tidyverse)
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))
by_day <- group_by(flights, year, month, day)
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE))

```
#5.6.1 Combining multiple operations with the pipe

```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE)
)
delay <- filter(delay, count > 20, dest != "HNL")
ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)

```

```{r}
delays <- flights %>% 
  group_by(dest) %>% 
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  filter(count > 20, dest != "HNL")

```

#5.6.2 Missing values

```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
head(flights)
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))

```

#5.6.3 Counts

```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay)
  )

ggplot(data = delays, mapping = aes(x = delay)) + 
  geom_freqpoly(binwidth = 10)

```

```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )

ggplot(data = delays, mapping = aes(x = n, y = delay)) + 
  geom_point(alpha = 1/10)

```

```{r}
batting <- as_tibble(Lahman::Batting)

batters <- batting %>% 
  group_by(playerID) %>% 
  summarise(
    ba = sum(H, na.rm = TRUE) / sum(AB, na.rm = TRUE),
    ab = sum(AB, na.rm = TRUE)
  )
batters %>% 
  filter(ab > 100) %>% 
  ggplot(mapping = aes(x = ab, y = ba)) +
    geom_point() + 
    geom_smooth(se = FALSE)
batters %>% 
  arrange(desc(ba))

```

#5.6.4 Useful summary functions

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0]) # the average positive delay
  )

```

```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(distance_sd = sd(distance)) %>% 
  arrange(desc(distance_sd))

```

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first = min(dep_time),
    last = max(dep_time)
  )

```

```{r}

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(hour_perc = mean(arr_delay > 60))
```

#5.6.5 Grouping by multiple variables

```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- summarise(daily, flights = n()))
(per_month <- summarise(per_day, flights = sum(flights)))
(per_year  <- summarise(per_month, flights = sum(flights)))

```

#5.6.6 Ungrouping

```{r}
daily %>% 
  ungroup() %>%             # no longer grouped by date
  summarise(flights = n()) 

```
#5.6.7 Exercises

1.Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:

A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.

A flight is always 10 minutes late.

A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.

99% of the time a flight is on time. 1% of the time it’s 2 hours late.

Which is more important: arrival delay or departure delay?
Delay type importance depends on individual preference.I think it depends on you for me I prefer to arrive on time so arrive delay is more important for me.
```{r}

#A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time
flights %>%
  group_by(flight) %>%
  summarize(early_15_min = sum(arr_delay <= -15, na.rm = TRUE) / n(),
            late_15_min = sum(arr_delay >= 15, na.rm = TRUE) / n()) %>%
  filter(early_15_min == 0.5,
         late_15_min == 0.5)

# A flight is always 10 minutes late.
flights %>%
  group_by(flight) %>%
  summarize(late_10 = sum(arr_delay == 10, na.rm = TRUE) / n()) %>%
  filter(late_10 == 1)

#A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.
flights %>%
  group_by(flight) %>%
  summarize(early_30_min = sum(arr_delay <= -30, na.rm = TRUE) / n(),
            late_30_min = sum(arr_delay >= 30, na.rm = TRUE) / n()) %>%
  filter(early_30_min == 0.5,
         late_30_min == 0.5)

#99% of the time a flight is on time. 1% of the time it’s 2 hours late
flights %>%
  group_by(flight) %>%
  summarize(on_time = sum(arr_delay == 0, na.rm = TRUE) / n(),
            late_2_hours = sum(arr_delay >= 120, na.rm = TRUE) / n()) %>%
  filter(on_time == .99,
         late_2_hours == .01)

```

2.Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
#first
not_cancelled %>%
  count(dest)
#new
not_cancelled %>%
  group_by(dest) %>%
  summarize(n = n())

#first
not_cancelled %>%
  count(tailnum, wt = distance)

#new
not_cancelled %>%
  group_by(tailnum) %>%
  summarize(n = sum(distance, na.rm = TRUE))

```

3.Our definition of cancelled flights (is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?

There are no flights which arrived but did not depart, so we can just use !is.na(dep_delay).

4.Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?

```{r}
flights %>%
  filter(is.na(dep_delay)) %>%
  count(day)
flights %>%
  group_by(day) %>%
  summarize(prop_canceled = sum(is.na(dep_delay)) / n(),
            avg_delay = mean(dep_delay, na.rm = TRUE))
```

5.Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))

```{r}
flights %>%
  group_by(carrier) %>%
  summarize(mean_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(mean_delay))
# challenge: bad airports vs. bad carriers
flights %>%
  group_by(carrier, dest) %>%
  summarize(mean_delay = mean(arr_delay, na.rm = TRUE)) %>%
  group_by(carrier) %>%
  summarize(mean_delay_mad = mad(mean_delay, na.rm = TRUE)) %>%
  arrange(desc(mean_delay_mad))
```

6.What does the sort argument to count() do. When might you use it?

The sort argument will sort the results of count() in descending order of n. This saves you a line of code.

#5.7 Grouped mutates (and filters)

```{r}
#Find all groups bigger than a threshold:

popular_dests <- flights %>% 
  group_by(dest) %>% 
  filter(n() > 365)
popular_dests

```
#5.7.1 Exercises

1.Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.

```{r}
?mutate

```

2.Which plane (tailnum) has the worst on-time record?
I define “on-time” in this function as arriving within 30 minutes of the scheduled arrival time.

```{r}
flights %>%
  group_by(tailnum) %>%
  summarize(prop_on_time = sum(arr_delay <= 30, na.rm = TRUE) / n(),
            mean_arr_delay = mean(arr_delay, na.rm = TRUE),
            flights = n()) %>%
  arrange(prop_on_time, desc(mean_arr_delay))
```

3.What time of day should you fly if you want to avoid delays as much as possible?

```{r}
flights %>%
  group_by(hour) %>%
  summarize(arr_delay = sum(arr_delay > 5, na.rm = TRUE) / n()) %>%
  ggplot(aes(x = hour, y = arr_delay)) +
  geom_col()
```
Avoid flying in the evening to minimize your arrival delay.

4.For each destination, compute the total minutes of delay. For each, flight, compute the proportion of the total delay for its destinatio

5.Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using lag() explore how the delay of a flight is related to the delay of the immediately preceding flight.

```{r}
flights %>%
  group_by(origin) %>%
  arrange(year, month, day, hour, minute) %>%
  mutate(prev_dep_delay = lag(dep_delay)) %>%
  ggplot(aes(x = prev_dep_delay, y = dep_delay)) +
  geom_point() +
  geom_smooth()
```
6.Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?

7.Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.

8.For each plane, count the number of flights before the first delay of greater than 1 hour
I have no idea
```
#6 Workflow: scripts

#6.2 RStudio diagnostics
cmd+shift+m gives the pipe (%>%)
cmd+shift+n gives new tab

