---
title: "R-club-May-10"
author: "Hajar"
date: "May 8, 2017"
output: 
  html_document: 
    keep_md: yes
---
```{r}
#install.packages("nycflights13")
library(nycflights13)
library(tidyverse)
nycflights13::flights

```

#5.1.3 dplyr basics

```{r}
filter(flights, arr_delay >= 120)

```

#5.2 Filter rows with filter()

```{r}
filter(flights, month == 1, day == 1)
jan1 <- filter(flights, month == 1, day == 1)

```

#5.2.1 Comparisons

```{r}
filter(flights, month == 1)

```

#5.2.2 Logical operators
```{r}
filter(flights, month == 11 | month == 12)
filter(flights, month == 11 | 12) # it doesn't work
nov_dec <- filter(flights, month %in% c(11, 12))
filter(flights, !(arr_delay > 120 | dep_delay > 120))
filter(flights, arr_delay <= 120, dep_delay <= 120)

```

#5.2.3 Missing values

```{r}
NA > 5
x <- NA
y <- NA
x == y
is.na(x)
df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)
filter(df, is.na(x) | x > 1)

```

#5.2.4 Exercises
1.Find all flights that
Had an arrival delay of two or more hours

```{r}
filter(flights, arr_delay >= 120)
```
Flew to Houston (IAH or HOU)
```{r}
filter(flights, dest == "IAH" | dest == "HOU")
```
Were operated by United, American, or Delta
```{r}
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```
Departed in summer (July, August, and September)
```{r}
filter(flights, month >= 7, month <= 9)
```
Arrived more than two hours late, but didn’t leave late
```{r}
filter(flights, arr_delay >= 120, dep_delay <= 0)
```
Were delayed by at least an hour, but made up over 30 minutes in flight
```{r}
filter(flights, dep_delay >= 60, dep_delay - arr_delay >= 30)

```
Departed between midnight and 6am (inclusive)
```{r}
filter(flights, dep_time >=0, dep_time <= 600)

```
2.Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
It is a shortcut for finding observations between two values.
```{r}
filter(flights, month >= 7, month <= 9)
filter(flights, between(month, 7, 9))

```

3.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
They are also missing values for arrival time and departure/arrival delay
```{r}
filter(flights, is.na(dep_time))

```

4.Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)
-NA ^ 0 -anything to the 0th power is 1.
NA | TRUE - as long as one condition is TRUE, the result is TRUE, TRUE is  TRUE.
FALSE & NA - NA indicates the absence of a value, so the conditional expression ignores it.
In general any operation on a missing value becomes a missing value. Hence NA * 0 is NA.
missing values are simply ignored

#5.3 Arrange rows with arrange()

```{r}
arrange(flights, year, month, day)
arrange(flights, desc(arr_delay))
df <- tibble(x = c(5, 2, NA))
arrange(df, x)
arrange(df, desc(x))

```
5.3.1 Exercises
How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).

```{r}
arrange(flights, !is.na(dep_time))

```

2.Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
#most delayed (based on arrival)
arrange(flights, desc(arr_delay))
# left earliest
arrange(flights, dep_delay)

```

3.Sort flights to find the fastest flights.
```{r}
arrange(flights, desc(distance / air_time))

```
4.Which flights travelled the longest? Which travelled the shortest?
```{r}
# longest flights by distance
arrange(flights, desc(distance))
# shortest flights by distance
arrange(flights, distance)

```
#5.4 Select columns with select()

```{r}
# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
?select
rename(flights, tail_num = tailnum)
select(flights, time_hour, air_time, everything())

```
5.4.1 Exercises

1.Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, starts_with("dep"), starts_with("arr"))
select(flights, contains("delay"))

```
2.What happens if you include the name of a variable multiple times in a select() call?
It is included only a single time in the new data frame.

3.What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
#It selects any variable which matches one of the strings in the vector.
variables <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(variables))

```

4.Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("TIME"))

select(flights, contains("TIME", ignore.case = FALSE))

```
#5.5 Add new variables with mutate()
```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)

#If you only want to keep the new variables, use transmute():

transmute(flights,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```
5.5.1 Useful creation functions
```{r}
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)

```
```{r}
x <- 1:10
lag(x)
lead(x)
row_number(y)
dense_rank(y)
percent_rank(y)
cume_dist(y)

```

5.5.2 Exercises
1.Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
transmute(flights,
       sched_dep_time = (sched_dep_time %/% 100) * 60 + sched_dep_time %% 100,
       dep_time = (dep_time %/% 100) * 60 + dep_time %% 100)
```
2.Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
```{r}
flights2 <- select(flights, air_time, arr_time, dep_time)
mutate(flights2, air_time_new = arr_time - dep_time)
```
They are not the same because dep_time and arr_time are not measured in minutes, but are numerical representations of the time. We need to convert them to continuous numbers like above to make the correct calculation for air_time.

3.Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?

dep_time should equal sched_dep_time + dep_delay (after accounting for the fact that they are not stored continuously).

4.Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().
```{r}
delayed <- mutate(flights, most_delayed = min_rank(desc(arr_delay)))
arrange(delayed, most_delayed)
```
I used min_rank() which assigns ties to the lowest rank. 

5.What does 1:3 + 1:10 return? Why?
```{r}
1:3 + 1:10
```
Because the two vectors are not the same length, R R adds the first elements together, then the second elements, then the third, etc until shorter vector is the same length.

6.What trigonometric functions does R provide?
Cosine, sine, tangent, arc-tangent, arc-sine, arc-tangent, and the two-argument arc-tangent.



