

---
title: "R-Club-Sep-6"
author: "Hajar"
date: "9/3/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#21 Iteration

```{r}
library(tidyverse)
```

#21.2 For loops
```{r}
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)

median(df$a)
#> [1] -0.246
median(df$b)
#> [1] -0.287
median(df$c)
#> [1] -0.0567
median(df$d)

#using loop
output <- vector("double", ncol(df))  # 1. output
for (i in seq_along(df)) {            # 2. sequence
  output[[i]] <- median(df[[i]])      # 3. body
}
output


y <- vector("double", 0)
seq_along(y)
#> integer(0)
1:length(y) # not understand this function
#> [1] 1 0
```

#21.2.1 Exercises

1.Write for loops to:

```{r}
#1.Compute the mean of every column in mtcars
df<-mtcars
output <-  vector("double", ncol(df))
for (i in seq_along(df)) {            # 2. sequence
  output[[i]] <- median(df[[i]])      # 3. body
}
output
colnames(mtcars)
```

```{r}
#2.Determine the type of each column in nycflights13::flights.
df <- nycflights13::flights
output <-  vector("list", ncol(df))
names(output) <- names(df)
for (i in seq_along(df)) {          
  output[[i]] <- class(df[[i]])      
}
output
```

```{r}
#3.Compute the number of unique values in each column of iris.
df <- iris
output <- vector("double", ncol(df))
names(output) <- names(df)
for(i in seq_along(df)) {
  output[[i]] <- length(unique(df[[i]]))
}
output
```

```{r}
#4.Generate 10 random normals for each of μ -10 0 10 100  
df <- c(-10, 0, 10, 100)
output <- vector("list" , length(df))
for( i in seq_along(df)) {
  output[[i]] <- mean(df[[i]])
}
output

#it is not complete

```

2.Eliminate the for loop in each of the following examples by taking advantage of an existing function that works with vectors

```{r}
out <- ""
for (x in letters) {
  out <- stringr::str_c(out, x)
}
out

stringr::str_c(letters, collapse = "")
```

```{r}
x <- sample(100)
sd <- 0
for (i in seq_along(x)) {
  sd <- sd + (x[i] - mean(x)) ^ 2
}
sd <- sqrt(sd / (length(x) - 1))
sd

#just rename sd to sdd
x <- sample(100)
sdd <- 0
for (i in seq_along(x)) {
  sdd <- sdd + (x[i] - mean(x)) ^ 2
}
sdd <- sqrt(sdd / (length(x) - 1))
sdd

sqrt(sum ((x-mean(x)) ^2) / (length(x) -1))

```

```{r}
x <- runif(100)
out <- vector("numeric", length(x))
out[1] <- x[1]
for (i in 2:length(x)) {
  out[i] <- out[i - 1] + x[i]
}
out

#The code above is calculating a cumulative sum

all_equal(cumsum(x),out)
```

3.Combine your function writing and for loop skills:

1.Write a for loop that prints() the lyrics to the children’s song “Alice the camel”.
I dont know what is lyrics ...

2.Convert the nursery rhyme “ten in the bed” to a function. Generalise it to any number of people in any sleeping structure.

```{r}
#The lyrics for Ten in the Bed:

numbers <- c("ten", "nine", "eight", "seven", "six", "five",
             "four", "three", "two", "one")
#for (i in numbers) {
  #cat(str_c("There were ", i, " in the bed\n"))
  #cat("and the little one said\n")
 # if (i == "one") {
  #  cat("I'm lonely...")
 # } else {
  #  cat("Roll over, roll over\n")
  #  cat("So they all rolled over and one fell out.\n")
 # }
#  cat("\n")
#}
# got error
```

3.Convert the song “99 bottles of beer on the wall” to a function. Generalise to any number of any vessel containing any liquid on any surface.
i don't konw

4.It’s common to see for loops that don’t preallocate the output and instead increase the length of a vector at each step:

```{r}
output <- vector("integer", 0)
for (i in seq_along(x)) {
  output <- c(output, lengths(x[[i]]))
}
output
```

#21.3 For loop variations
#21.3.1 Modifying an existing object

```{r}
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}

df$a <- rescale01(df$a)
df$b <- rescale01(df$b)
df$c <- rescale01(df$c)
df$d <- rescale01(df$d)

 for(i in seq_along(df)) {
 df[[i]] <- rescale01(df[[i]])
}
```

#21.3.2 Looping patterns

```{r}
results <- vector("list", length(x))
names(results) <- names(x)
```

```{r}
for (i in seq_along(x)) {
  name <- names(x)[[i]]
  value <- x[[i]]
}
```

#21.3.3 Unknown output length

```{r}
means <- c(0, 1, 2)

output <- double()
for (i in seq_along(means)) {
  n <- sample(100, 1)
  output <- c(output, rnorm(n, means[[i]]))
}
str(output)
```

```{r}
out <- vector("list", length(means))
for (i in seq_along(means)) {
  n <- sample(100, 1)
  out[[i]] <- rnorm(n, means[[i]])
}
str(out)

str(unlist(out))

```

#21.3.4 Unknown sequence length

```{r}
#for (i in seq_along(x)) {
  # body
#}

# Equivalent to
#i <- 1
#while (i <= length(x)) {
  # body
  #i <- i + 1 
#}i

```

```{r}
flip <- function() sample(c("T", "H"), 1)

flips <- 0
nheads <- 0

while (nheads < 3) {
  if (flip() == "H") {
    nheads <- nheads + 1
  } else {
    nheads <- 0
  }
  flips <- flips + 1
}
flips
```

#21.3.5 Exercises

1.Imagine you have a directory full of CSV files that you want to read in. You have their paths in a vector, files <- dir("data/", pattern = "\\.csv$", full.names = TRUE), and now want to read each one with read_csv(). Write the for loop that will load them into a single data frame.

```{r}
files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)
df <- vector("list", length(files))
for (fname in seq_along(files)) {
  df[[i]] <- read_csv(files[[i]])
}
df <- bind_rows(df)
```

2.What happens if you use for (nm in names(x)) and x has no names? What if only some of the elements are named? What if the names are not unique?

```{r}
x <- 1:3
print(names(x))
#> NULL
for (nm in names(x)) {
  print(nm)
  print(x[[nm]])
}

length(NULL)

x <- c(a = 1, 2, c = 3)
names(x)

#for (nm in names(x)) {
  #print(nm)
  #print(x[[nm]])
#}

#> Error in x[[nm]]: subscript out of bounds
#Finally, if there are duplicate names, then x[[nm]] will give the first element with that name. There is no way to access duplicately named elements by name.

x <- c(a = 1, a = 2, c = 3)
names(x)

for (nm in names(x)) {
  print(nm)
  print(x[[nm]])
}
```

3.Write a function that prints the mean of each numeric column in a data frame, along with its name. For example, show_mean(iris) would print:

```{r}
#show_mean(iris)
#no idea
```

4.What does this code do? How does it work?

```{r}
trans <- list( 
  disp = function(x) x * 0.0163871,
  am = function(x) {
    factor(x, labels = c("auto", "manual"))
  }
)
for (var in names(trans)) {
  mtcars[[var]] <- trans[[var]](mtcars[[var]])
}
```
This code mutates the disp and am columns:

disp is multiplied by 0.0163871
am is replaced by a factor variable.
then with forloop calls the named function in the list on the column of mtcars with the same name, and replaces the values of that column.

```{r}
trans[["disp"]]

#This applies the function to the column of mtcars with the same name

trans[["disp"]](mtcars[["disp"]])
```

#21.4 For loops vs. functionals

```{r}
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)
```

```{r}
col_mean <- function(df) {
  output <- vector("double", length(df))
  for (i in seq_along(df)) {
    output[i] <- mean(df[[i]])
  }
  output
}
```

```{r}
col_median <- function(df) {
  output <- vector("double", length(df))
  for (i in seq_along(df)) {
    output[i] <- median(df[[i]])
  }
  output
}
col_sd <- function(df) {
  output <- vector("double", length(df))
  for (i in seq_along(df)) {
    output[i] <- sd(df[[i]])
  }
  output
}
```

```{r}
f1 <- function(x) abs(x - mean(x)) ^ 1
f2 <- function(x) abs(x - mean(x)) ^ 2
f3 <- function(x) abs(x - mean(x)) ^ 3
```

```{r}
f <- function(x, i) abs(x - mean(x)) ^ i

```

```{r}
col_summary <- function(df, fun) {
  out <- vector("double", length(df))
  for (i in seq_along(df)) {
    out[i] <- fun(df[[i]])
  }
  out
}
col_summary(df, median)
#> [1]  0.237 -0.218  0.254 -0.133
col_summary(df, mean)
#> [1]  0.2026 -0.2068  0.1275 -0.0917
```

#21.4.1 Exercises

1.Read the documentation for apply(). In the 2d case, what two for loops does it generalise?
t generalises looping over the rows or columns of a matrix or data-frame.

2.Adapt col_summary() so that it only applies to numeric columns You might want to start with an is_numeric() function that returns a logical vector that has a TRUE corresponding to each numeric column.

```{r}

```