---
title: "R-club-Jun-14"
author: "Hajar"
date: "June 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#12.2 Tidy data
```{r}
library(tidyverse)
table1 %>% 
  mutate(rate = cases / population * 10000)

table1 %>% 
  count(year, wt = cases)

library(ggplot2)
ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```
#12.2.1 Exercises
1.Using prose, describe how the variables and observations are organised in each of the sample tables.

```{r}
#In table1 each row is a (country, year) with variables cases and population.
table1

#In table2, each row is country, year , variable (“cases”, “population”) combination, and there is a count variable with the numeric value of the variable.
table2

#In table3, each row is a (country, year) combination with the column rate having the rate of cases to population 
table3

#Table 4 is split into two tables, one table for each variable: table4a is the table for cases, while table4b is the table for population. Within each table, each row is a country, each column is a year, and the cells are the value of the variable for the table.

table4a
table4b

```

2.Compute the rate for table2, and table4a + table4b. You will need to perform four operations:
  
1.Extract the number of TB cases per country per year.
2.Extract the matching population per country per year.
3.Divide cases by population, and multiply by 10000.
4.Store back in the appropriate place.
Which representation is easiest to work with? Which is hardest? Why?

```{r}
tb2_cases <- filter(table2, type == "cases")[["count"]]
tb2_country <- filter(table2, type == "cases")[["country"]]
tb2_year <- filter(table2, type == "cases")[["year"]]
tb2_population <- filter(table2, type == "population")[["count"]]
table2_clean <- tibble(country = tb2_country,
       year = tb2_year,
       rate = tb2_cases / tb2_population)
table2_clean

tibble(country = table4a[["country"]],
       `1999` = table4a[["1999"]] / table4b[["1999"]],
       `2000` = table4a[["2000"]] / table4b[["2000"]])
or
tibble(country = rep(table4a[["country"]], 2),
       year = rep(c(1999, 2000), each = nrow(table4a)),
       `rate` = c(table4a[["1999"]] / table4b[["1999"]],
                  table4a[["2000"]] / table4b[["2000"]]))
```
3.Recreate the plot showing change in cases over time using table2 instead of table1. What do you need to do first?
First, I needed to filter the tibble to only include those rows that represented the “cases” variable.

```{r}
table2 %>% 
  filter(type == "cases") %>%
  ggplot(aes(year, count)) + 
  geom_line(aes(group = country)) + 
  geom_point(aes(colour = country))
```

#12.3 Spreading and gathering
12.3.1 Gathering

```{r}
tidy4a <- table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")

tidy4b <- table4b %>% 
  gather(`1999`, `2000`, key = "year", value = "population")

left_join(tidy4a, tidy4b)

```
#12.3.2 Spreading

```{r}
table2
spread(table2, key = type, value = count)
```

#12.3.3 Exercises

1.Why are gather() and spread() not perfectly symmetrical?
Carefully consider the following example:
```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)

#The functions spread and gather are not perfectly symmetrical because column type information is not transferred between them. In the original table the column year was numeric, but after the spread-gather function it is character, because with gather, variable names are always converted to a character vector.

#Both spread() and gather() have a convert argument. What does it do?

#The convert argument tries to convert character vectors to the appropriate type. 

stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`, convert = TRUE)

```

2. Why does this code fail?

```{r}
#table4a %>% 
  gather(1999, 2000, key = "year", value = "cases")

#The code fails because the column names 1999 and 2000 are not standard and thus needs to be quoted. 

table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")

```
3.Why does spreading this tibble fail? How could you add a new column to fix the problem?

```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
#spread(people, key, value)

#Spreading the data frame fails because there are two rows with “age” for “Phillip Woods”. We would need to add another column with an indicator for the number observation it is,

people <- tribble(
  ~name,             ~key,    ~value, ~obs,
  #-----------------|--------|------|------
  "Phillip Woods",   "age",       45, 1,
  "Phillip Woods",   "height",   186, 1,
  "Phillip Woods",   "age",       50, 2,
  "Jessica Cordero", "age",       37, 1,
  "Jessica Cordero", "height",   156, 1
)

spread(people, key, value)

```
4.Tidy the simple tibble below. Do you need to spread or gather it? What are the variables?

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)

#You need to gather it. The variables are:
#pregnant: logical (“yes”, “no”)
#female: logical
#count: integer

gather(pregnant, sex, count, male, female) %>%
  mutate(pregnant = pregnant == "yes",
         female = sex == "female") %>%
  select(-sex)
#got error
```

#12.4 Separating and uniting
#12.4.1 Separate

```{r}
table3
table3 %>% 
  separate(rate, into = c("cases", "population"))

table3 %>% 
  separate(rate, into = c("cases", "population"), sep = "/")

table3 %>% 
  separate(rate, into = c("cases", "population"), convert = TRUE)

table3 %>% 
  separate(year, into = c("century", "year"), sep = 2)
```

#12.4.2 Unite

```{r}
table5 %>% 
  unite(new, century, year)

table5 %>% 
  unite(new, century, year, sep = "")

```

#12.4.3 Exercises

1.What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))

?separate
#The extra argument tells separate what to do if there are too many pieces, and the fill argument if there aren’t enough.

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))

#By default we got a warning.

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")

#without warning

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "left")

```

2.Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?
You would set it to FALSE if you want to create a new variable, but keep the old one.

3.Compare and contrast separate() and extract(), Why are there three variations of separation (by position, by separator, and with groups), but only one unite?
The function extract uses a regular expression to find groups and split into columns. 
In unite it is many columns to one, and once the columns are specified, there is only one way to do it, the only choice is the sep. In separate, there are multiple ways to split the character string.
