---
title: "R-Club-13-Sep"
author: "Hajar"
date: "9/11/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)
map_dbl(df, mean)
map_dbl(df, median)
map_dbl(df, sd)

df %>% map_dbl(mean)
df %>% map_dbl(median)
df %>% map_dbl(sd)


```


```{r}
map_dbl(df, mean, trim = 0.5)

```

```{r}
z <- list(x = 1:3, y = 4:5)
map_int(z, length)
```
#21.5.1 Shortcuts

```{r}
models <- mtcars %>% 
  split(.$cyl) %>% 
  map(function(df) lm(mpg ~ wt, data = df))

models <- mtcars %>% 
  split(.$cyl) %>% 
  map(~lm(mpg ~ wt, data = .))

models %>% 
  map(summary) %>% 
  map_dbl(~.$r.squared)
#number of 4 6 8 is for cyl

models %>% 
  map(summary) %>% 
  map_dbl("r.squared")
#same result
```

```{r}
x <- list(list(1, 2, 3), list(4, 5, 6), list(7, 8, 9))
x %>% map_dbl(2)
```

#21.5.2 Base R

```{r}
x1 <- list(
  c(0.27, 0.37, 0.57, 0.91, 0.20),
  c(0.90, 0.94, 0.66, 0.63, 0.06), 
  c(0.21, 0.18, 0.69, 0.38, 0.77)
)
x2 <- list(
  c(0.50, 0.72, 0.99, 0.38, 0.78), 
  c(0.93, 0.21, 0.65, 0.13, 0.27), 
  c(0.39, 0.01, 0.38, 0.87, 0.34)
)
threshold <- function(x, cutoff = 0.8) x[x > cutoff]
x1 %>% sapply(threshold) %>% str()
x2 %>% sapply(threshold) %>% str()

```

#21.5.3 Exercises

1.Write code that uses one of the map functions to:
1.Compute the mean of every column in mtcars.

```{r}
output <- vector("double", ncol(mtcars))
names(output) <- names(mtcars)
for (i in names(mtcars)) {
  output[i] <- mean(mtcars[[i]])
}
output

map_dbl(mtcars, mean)

```

2.Determine the type of each column in nycflights13::flights.

```{r}
data("flights", package = "nycflights13")
output <- vector("list", ncol(flights))
names(output) <- names(flights)
for (i in names(flights)) {
  output[[i]] <- class(flights[[i]])
}
output

map(nycflights13::flights, class)

map_chr(nycflights13::flights, typeof)


```

3.Compute the number of unique values in each column of iris.

```{r}
data(iris)
iris_uniq <- vector("double", ncol(iris))
names(iris_uniq) <- names(iris)
for (i in names(iris)) {
  iris_uniq[i] <- length(unique(iris[[i]]))
}
iris_uniq

map_int(iris, ~ length(unique(.)))

```

4.Generate 10 random normals for each of 

```{r}
# number to draw
n <- 10
# values of the mean
mu <- c(-10, 0, 10, 100)
normals <- vector("list", length(mu))
for (i in seq_along(normals)) {
  normals[[i]] <- rnorm(n, mean = mu[i])
}
normals

matrix(rnorm(n * length(mu), mean = mu), ncol = n)

map(c(-10, 0, 10, 100), rnorm, n = 10)

```

2.How can you create a single vector that for each column in a data frame indicates whether or not it’s a factor?

```{r}
map_lgl(mtcars, is.factor)
```

3.What happens when you use the map functions on vectors that aren’t lists? What does map(1:5, runif) do? Why?

```{r}
map(1:5, runif)

```

4.What does map(-2:2, rnorm, n = 5) do? Why? What does map_dbl(-2:2, rnorm, n = 5) do? Why?

```{r}
#This takes samples of n = 5 from normal distributions of means -2, -1, 0, 1, and 2, and returns a list with each element a numeric vectors of length 5.

map(-2:2, rnorm, n = 5)
```

5.Rewrite map(x, function(df) lm(mpg ~ wt, data = df)) to eliminate the anonymous function.

```{r}
map(list(mtcars), ~ lm(mpg ~ wt, data = .))
```

#21.6 Dealing with failure
```{r}
safe_log <- safely(log)
str(safe_log(10))
str(safe_log("a"))

```

```{r}
x <- list(1, 10, "a")
y <- x %>% map(safely(log))
str(y)

```

```{r}
y <- y %>% transpose()
str(y)
```

```{r}
purrr::transpose
is_ok <- y$error %>% map_lgl(is_null)
#x[!is_ok]

#y$result[is_ok] %>% flatten_dbl()
```

```{r}
x <- list(1, 10, "a")
x %>% map_dbl(possibly(log, NA_real_))
```

```{r}
x <- list(1, -1)
x %>% map(quietly(log)) %>% str()
```

#21.7 Mapping over multiple arguments

```{r}
mu <- list(5, 10, -3)
mu %>% 
  map(rnorm, n = 5) %>% 
  str()
```

```{r}
sigma <- list(1, 5, 10)
seq_along(mu) %>% 
  map(~rnorm(5, mu[[.]], sigma[[.]])) %>% 
  str()
# let me know more about .

map2(mu, sigma, rnorm, n = 5) %>% str()

```

```{r}
map2 <- function(x, y, f, ...) {
  out <- vector("list", length(x))
  for (i in seq_along(x)) {
    out[[i]] <- f(x[[i]], y[[i]], ...)
  }
  out
}
```

```{r}
n <- list(1, 3, 5)
args1 <- list(n, mu, sigma)
args1 %>%
  pmap(rnorm) %>% 
  str()
```

```{r}
args2 <- list(mean = mu, sd = sigma, n = n)
args2 %>% 
  pmap(rnorm) %>% 
  str()
```

```{r}
params <- tribble(
  ~mean, ~sd, ~n,
    5,     1,  1,
   10,     5,  3,
   -3,    10,  5
)
params %>% 
  pmap(rnorm)
```

#21.7.1 Invoking different functions

```{r}
f <- c("runif", "rnorm", "rpois")
param <- list(
  list(min = -1, max = 1), 
  list(sd = 5), 
  list(lambda = 10)
)
```

```{r}
f <- c("runif", "rnorm", "rpois")
param <- list(
  list(min = -1, max = 1), 
  list(sd = 5), 
  list(lambda = 10)
)
invoke_map(f, param, n = 5) %>% str()

```

```{r}
sim <- tribble(
  ~f,      ~params,
  "runif", list(min = -1, max = 1),
  "rnorm", list(sd = 5),
  "rpois", list(lambda = 10)
)
#sim %>% 
 # mutate(sim = invoke_map(f, params, n = 10))
 # got error?????
```

#21.8 Walk

```{r}
x <- list(1, "a", 3)

x %>% 
  walk(print)
```

```{r}
library(ggplot2)
plots <- mtcars %>% 
  split(.$cyl) %>% 
  map(~ggplot(., aes(mpg, wt)) + geom_point())
paths <- stringr::str_c(names(plots), ".pdf")

pwalk(list(paths, plots), ggsave, path = tempdir())
```


#21.9.3 Exercises

1.Implement your own version of every() using a for loop. Compare it with purrr::every(). What does purrr’s version do that your version doesn’t?
..

2.Create an enhanced col_sum() that applies a summary function to every numeric column in a data frame.

```{r}
#I will use map to apply the function to all the columns, and keep to only select numeric columns.

col_sum2 <- function(df, f, ...) {
  map(keep(df, is.numeric), f, ...)
}
col_sum2(iris, mean)
```


3.A possible base R equivalent of col_sum() is:

```{r}
col_sum3 <- function(df, f) {
  is_num <- sapply(df, is.numeric)
  df_num <- df[, is_num]

  sapply(df_num, f)
}
#But it has a number of bugs as illustrated with the following inputs:

df <- tibble(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)
# OK
col_sum3(df, mean)
# Has problems: don't always return numeric vector
col_sum3(df[1:2], mean)
col_sum3(df[1], mean)
#col_sum3(df[0], mean)

#What causes the bugs?
```

The problem is that sapply doesn’t always return numeric vectors. If no columns are selected, instead of exiting, it returns an empty list. This causes an error since we can’t use a list with [.

```{r}
sapply(df[0], is.numeric)

sapply(df[1], is.numeric)

sapply(df[1:2], is.numeric)
```

