---
title: "R-club-May-24"
author: "Hajar"
date: "5/19/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
#library(tidyverse)

```
#7.2 Questions
#7.3.1 Visualising distributions

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))

```

```{r}
diamonds %>% 
  count(cut)

```

```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = carat), binwidth = 0.5)

```

```{r}
diamonds %>% 
  count(cut_width(carat, 0.5))
```

#zome in particular data

```{r}
smaller <- diamonds %>% 
  filter(carat < 3)
  
ggplot(data = smaller, mapping = aes(x = carat)) +
  geom_histogram(binwidth = 0.1)

```

```{r}
ggplot(data = smaller, mapping = aes(x = carat, colour = cut)) +
  geom_freqpoly(binwidth = 0.1)

```

```{r}
ggplot(data = smaller, mapping = aes(x = carat)) +
  geom_histogram(binwidth = 0.01)
```

```{r}
ggplot(data = faithful, mapping = aes(x = eruptions)) + 
  geom_histogram(binwidth = 0.25)

```

#7.3.3 Unusual values

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5)

```

```{r}
unusual <- diamonds %>% 
  filter(y < 3 | y > 20) %>% 
  select(price, x, y, z) %>%
  arrange(y)
unusual

```

#7.3.4 Exercises

1.Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

```{r}
ggplot(diamonds, aes(x)) +
  geom_histogram()

ggplot(diamonds, aes(y)) +
  geom_histogram()

ggplot(diamonds, aes(z)) +
  geom_histogram()

```

2.Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)

```{r}
# I used default binwidth
ggplot(diamonds, aes(price)) +
  geom_histogram()

# binwidth = 100
ggplot(diamonds, aes(price)) +
  geom_histogram(binwidth = 100) +
  scale_x_continuous(breaks = seq(0, 20000, by = 1000))
#I want to know much closer price to $1500,by defualt it is not obvious

```

3.How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?
```{r}
ggplot(diamonds, aes(carat)) +
  geom_histogram(binwidth = .01) +
  coord_cartesian(xlim = c(.97, 1.03))


```

4.Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?

```{r}
# full plot
ggplot(diamonds, aes(carat, price)) +
  geom_point() +
  geom_smooth()

#xlim
ggplot(diamonds, aes(carat, price)) +
  geom_point() +
  geom_smooth() +
  xlim(1, 3)

# coord_cartesian
ggplot(diamonds, aes(carat, price)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(xlim = c(1, 3))

```

#7.4 Missing values

```{r}
diamonds2 <- diamonds %>% 
  filter(between(y, 3, 20))
diamonds2

```

```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))
diamonds

```

```{r}

ggplot(data = diamonds2, mapping = aes(x = x, y = y)) + 
  geom_point()

ggplot(data = diamonds2, mapping = aes(x = x, y = y)) + 
  geom_point(na.rm = TRUE)

```

```{r}

nycflights13::flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>% 
   ggplot(mapping = aes(sched_dep_time)) + 
    geom_freqpoly(mapping = aes(colour = cancelled), binwidth = 1/4)

```

#7.4.1 Exercises

1.What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?

```{r}
ggplot(flights, aes(dep_delay)) +
  geom_histogram()

# change AA to NA
flights %>%
  mutate(carrier = ifelse(carrier == "AA", NA, carrier)) %>%
  ggplot(aes(carrier)) +
  geom_bar()

```
Histograms omit missing values, whereas bar charts draw them as a separate category. 

2.What does na.rm = TRUE do in mean() and sum()?
It strips missing values before computing the statistic.

#7.5 Covariation

7.5.1 A categorical and continuous variable

```{r}
ggplot(data = diamonds, mapping = aes(x = price)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)

ggplot(diamonds) + 
  geom_bar(mapping = aes(x = cut))

ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)

```

```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_boxplot()

```

```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) +
  geom_boxplot()

```

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy))
```

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy)) +
  coord_flip()

```

#7.5.1.1 Exercises
1.Use what you’ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights.

```{r}
# original chart
flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
    ) %>%
  ggplot(mapping = aes(sched_dep_time)) + 
  geom_freqpoly(mapping = aes(colour = cancelled), binwidth = 1/4)

# revised chart
flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
    ) %>%
  ggplot(aes(x = sched_dep_time, y = ..density.., color = cancelled)) + 
  geom_freqpoly(binwidth = 1/4)

```

2.What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?

```{r}
ggplot(diamonds, aes(carat, price)) +
  geom_point() +
  geom_smooth()

#Carat size is the most important predictor of price.

ggplot(diamonds, aes(cut, carat)) +
  geom_boxplot()

#This boxplot visualizes the relationship between cut and carat. On average, fair and good cut diamonds are larger than premium and ideal cuts. If carat size is the more dominant predictor of price, then some larger good cut diamonds will be more expensive than smaller ideal cut diamonds.
```

3.Install the ggstance package, and create a horizontal boxplot. How does this compare to using coord_flip()?

```{r}
install.packages("ggstance")

#in ggplot2 with coord_flip(), I supply aesthetics as if they were to be drawn vertically
ggplot(diamonds, aes(cut, carat)) +
  geom_boxplot() +
  coord_flip()

```

4.One problem with boxplots is that they were developed in an era of much smaller datasets and tend to display a prohibitively large number of “outlying values”. One approach to remedy this problem is the letter value plot. Install the lvplot package, and try using geom_lv() to display the distribution of price vs cut. What do you learn? How do you interpret the plots?

```{r}
devtools::install_github("hadley/lvplot")
library(lvplot)

# with boxplot
ggplot(diamonds, aes(cut, price)) +
  geom_boxplot()

# with lvplot
ggplot(diamonds, aes(cut, price)) +
  geom_lv()

```

5.Compare and contrast geom_violin() with a facetted geom_histogram(), or a coloured geom_freqpoly(). What are the pros and cons of each method?


