---
title: "R-Club-Nov-8"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(modelr)
options(na.action = na.warn)
library("broom")

library(nycflights13)
library(lubridate)
```

```{r}
diamonds2 <- diamonds %>% 
  filter(carat <= 2.5) %>% 
  mutate(lprice = log2(price), lcarat = log2(carat))

mod_diamond2 <- lm(lprice ~ lcarat + color + cut + clarity, data = diamonds2)
```

#24.2.3 Exercises
1.In the plot of lcarat vs. lprice, there are some bright vertical strips. What do they represent?
The distribution of diamonds has more diamonds at round or otherwise human friendly numbers (fractions).

2-If log(price) = a_0 + a_1 * log(carat), what does that say about the relationship between price and carat?
An 1% increase in carat is associated with an  a1a1 % increase in price.

3.Extract the diamonds that have very high and very low residuals. Is there anything unusual about these diamonds? Are the particularly bad or good, or do you think these are pricing errors?

4.Does the final model, mod_diamonds2, do a good job of predicting diamond prices? Would you trust it to tell you how much to spend if you were buying a diamond?

```{r}
diamonds2 %>% 
  add_predictions(mod_diamond2) %>%
  add_residuals(mod_diamond2) %>%
  summarise(sq_err = sqrt(mean(resid^2)),
            abs_err = mean(abs(resid)),
            p975_err = quantile(resid, 0.975),
            p025_err = quantile(resid, 0.025))


```

#24.3

```{r}
library("nycflights13")
daily <- flights %>% 
  mutate(date = make_date(year, month, day)) %>% 
  group_by(date) %>% 
  summarise(n = n())

daily
ggplot(daily, aes(date, n)) + 
  geom_line()
```

24.3.1

```{r}
daily <- daily %>% 
  mutate(wday = wday(date, label = TRUE))
ggplot(daily, aes(wday, n)) + 
  geom_boxplot()
```

```{r}
mod <- lm(n ~ wday, data = daily)

grid <- daily %>% 
  data_grid(wday) %>% 
  add_predictions(mod, "n")

ggplot(daily, aes(wday, n)) + 
  geom_boxplot() +
  geom_point(data = grid, colour = "red", size = 4)
```

```{r}
daily <- daily %>% 
  add_residuals(mod)
daily %>% 
  ggplot(aes(date, resid)) + 
  geom_ref_line(h = 0) + 
  geom_line()
```

```{r}
ggplot(daily, aes(date, resid, colour = wday)) + 
  geom_ref_line(h = 0) + 
  geom_line()
```

```{r}
daily %>% 
  filter(resid < -100)
```

```{r}
daily %>% 
  ggplot(aes(date, resid)) + 
  geom_ref_line(h = 0) + 
  geom_line(colour = "grey50") + 
  geom_smooth(se = FALSE, span = 0.20)
```

#24.3.2

```{r}
daily %>% 
  filter(wday == "Sat") %>% 
  ggplot(aes(date, n)) + 
    geom_point() + 
    geom_line() +
    scale_x_date(NULL, date_breaks = "1 month", date_labels = "%b")
```

```{r}
term <- function(date) {
  cut(date, 
    breaks = ymd(20130101, 20130605, 20130825, 20140101),
    labels = c("spring", "summer", "fall") 
  )
}

daily <- daily %>% 
  mutate(term = term(date)) 

daily %>% 
  filter(wday == "Sat") %>% 
  ggplot(aes(date, n, colour = term)) +
  geom_point(alpha = 1/3) + 
  geom_line() +
  scale_x_date(NULL, date_breaks = "1 month", date_labels = "%b")
```

