---
title: "R-club-Apr-26"
output:
  pdf_document: default
  html_document:
    keep_md: yes
    toc: yes
---
#3.1.1 Prerequisites
```{r}
#install.packages(tidyverse)
library(tidyverse)
library(ggplot2)
```
#3.2.2 Creating a ggplot
```{r}
mpg
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
#3.2.3 A graphing template
##3.2.4 Exercises
###1.Run ggplot(data = mpg) what do you see?
```{r}
ggplot(data = mpg)# I see nothing
```
###2.How many rows are in mtcars? How many columns?
```{r}
dim(mtcars) # 32 11 number of row equal to "32" & number of col equal to "11"
ncol(mtcars) #number of col equal to "11"
```
###3.What does the drv variable describe? Read the help for ?mpg to find out.
```{r}
?mpg
#$f describe front-wheel drive, r = rear wheel drive, 4 = 4wd
```
###4.Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))
```
###5.What happens if you make a scatterplot of class vs drv. Why is the plot not useful?
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv)) 
#it has no  meaning to me
```
#3.3 Aesthetic mappings
##3.3.1 Exercises
###1.What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
#in this function the colour does not change, if I want to change the color it must not be in aes()
```
###2.Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r}
?mpg
mpg
#manufacturer,model,trans,drv, fl, and class are categorials
##displ, year, cyl, cty, and hwy are continuous
# also we can check this with see the distribution 
hist(mpg$displ) # as categorials
hist(mpg$hwy)# as continuous normal distribution
```
###3.Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
#color
mpg
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cyl))
#since colors are continuous, so it is hard to explain the difference between continuous variables
###size
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cyl))
###shape
#mpg #it is wrong the continuous variable can not be mapped to shape
#ggplot(data = mpg) + 
#geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```
###4.What happens if you map the same variable to multiple aesthetics?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = cyl, color = cyl))
# I get a nice  correlation line
```
###5.What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy,color = model), stroke = 1)
?geom_point
#change the size of the points in the plot
```
###6.What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy,color = cyl < 5), stroke = 1)
```
#3.4 Common problems
#3.5 Facets
##3.5.1 Exercises
###1.What happens if you facet on a continuous variable?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cyl, nrow = 2)
```
###2.What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
#there are no points for x and y combination such as there are no points fordrv= 4 and cyl=5
```
###3.What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
#facet only in y axis
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
#facet only in x axis
```
###4.Take the first faceted plot in this section
###What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color=class)) + 
  facet_wrap(~ class, nrow = 2)
#Advantages: if I have a large data for analyzing it is easy to use colour as we can see in this function. also this function give us more information #disadvantages: becuase we don't have a largest dataset there is no strong negative relationship between displ and hwy
### How might the balance change if you had a larger dataset?
#Each figure may have a strong negative relationships between displ and hwy.

###5.Read ?facet_wrap. What does nrow do? What does ncol do? 
#nrow represented num of rows and ncol represented the number of columns in facet_warp.
###5.What other options control the layout of the individual panels? 
#threre are several options such as  labeller, as.table
#Try as.table. If the default TRUE, the facets look like a table with highest values at the bottom-right. If FALSE, the facets look like a plot with the highest value at the top-right.
#5.Why doesn’t facet_grid() have nrow and ncol variables?
#becuase it was faceted according to the levels of variables.

###6.When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
?facet_grid
#if put variables with less unique levels, the plots would have many grids so it would not be appropriate for understanding.
```