---
title: "ISLR_club_6_Dec"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#3.6.1 Libraries
```{r}
library (MASS)
library (ISLR)

```
#3.6.2 Simple Linear Regression
```{r}
fix(Boston)
names(Boston)
#lm.fit =lm(medv∼lstat)
lm.fit <- lm(medv~lstat, data = Boston)
attach (Boston )
lm.fit <- lm(medv~lstat)
lm.fit
summary(lm.fit)
names(lm.fit)
coef(lm.fit)
confint (lm.fit)
predict (lm.fit ,data.frame(lstat=c(5 ,10 ,15)),interval ="confidence")
predict (lm.fit ,data.frame(lstat=c(5 ,10 ,15)),interval ="prediction")
plot(lstat,medv)
x <- plot(lstat,medv)
abline(lm.fit)
abline (lm.fit ,lwd =3)
abline (lm.fit ,lwd =3, col ="red")
plot(lstat ,medv ,col ="red ")
plot(lstat ,medv ,pch =20)
plot(lstat ,medv ,pch ="+")
plot (1:20 ,1:20, pch =1:20)
par(mfrow =c(2,2))
plot(lm.fit)
plot(predict (lm.fit), residuals (lm.fit))
plot(predict (lm.fit), rstudent (lm.fit))
plot(hatvalues (lm.fit ))
which.max (hatvalues (lm.fit))
```
#3.7 Exercises

3.Suppose we have a data set with five predictors, X1 =GPA, X2 = IQ,
X3 = Gender (1 for Female and 0 for Male), X4 = Interaction between
GPA and IQ, and X5 = Interaction between GPA and Gender. The
response is starting salary after graduation (in thousands of dollars).
Suppose we use least squares to fit the model, and get ˆβ0 = 50, ˆβ1 =
20, ˆβ2 = 0.07, ˆβ3 = 35, ˆβ4 = 0.01, ˆβ5 = −10.
(a) Which answer is correct, and why?
i. For a fixed value of IQ and GPA, males earn more on average
than females.
 



ii. For a fixed value of IQ and GPA, females earn more on
average than males.
iii. For a fixed value of IQ and GPA, males earn more on average
than females provided that the GPA is high enough.
iv. For a fixed value of IQ and GPA, females earn more on
average than males provided that the GPA is high enough.

answer:
Y = 50 + 20(gpa) + 0.07(iq) + 35(gender) + 0.01(gpa * iq) - 10 (gpa * gender)
suppose : gpa l1 iq l2
(a) Y = 50 + 20 l1 + 0.07 l2 + 35 gender + 0.01(l1 * l2) - 10 (l1 * gender)
male: (gender = 0)   50 + 20 l1 + 0.07 l2 + 0.01(l1 * l2)
female: (gender = 1) 50 + 20 l1 + 0.07 l2 + 35 + 0.01(l1 * l2) - 10 (l1)
iii. Once the GPA is high enough, males earn more on average.

(b) Predict the salary of a female with IQ of 110 and a GPA of 4.0.

answer:
(b) Y(Gender = 1, IQ = 110, GPA = 4.0)
= 50 + 20 * 4 + 0.07 * 110 + 35 + 0.01 (4 * 110) - 10 * 4
= 137.1

(c) True or false: Since the coefficient for the GPA/IQ interaction
term is very small, there is very little evidence of an interaction
effect. Justify your answer.

answer:
(c) False. We must examine the p-value of the regression coefficient to
understand whether the interaction term is statistically significant or not.

8. This question involves the use of simple linear regression on the Auto
data set.
(a) Use the lm() function to perform a simple linear regression with
mpg as the response and horsepower as the predictor. Use the
summary() function to print the results. Comment on the output.
For example:
i. Is there a relationship between the predictor and the response?
ii. How strong is the relationship between the predictor and
the response?
iii. Is the relationship between the predictor and the response
positive or negative?
iv. What is the predicted mpg associated with a horsepower of
98? What are the associated 95% confidence and prediction
intervals?

```{r}
data(Auto)
summary(Auto)
attach(Auto)
lm.fit = lm(mpg ~ horsepower)
summary(lm.fit)

#i.Yes, there is a relationship between horsepower and mpg as deterined by testing the null hypothesis of coefficients equal to zero. we can see the F is latder than 1 and p-value of the F-statistic is close to zero we can reject the null hypothesis.

#ii.To calculate the residual error relative to the response we use the mean of the response and the RSE.The RSE of the lm.fit was  4.906 which indicates a percentage error of  4.906/mean(mpg, na.rm=T) * 100.0%. The R^2 of the lm.fit was about 0.60 60% of the variance in mpg is explained by horsepower.

#iii.The relationship between mpg and horsepower is negative. The more horsepower the less mpg fuel efficiency 

#iv.
predict(lm.fit, data.frame(horsepower=c(98)), interval="confidence")
#       fit      lwr      upr
#1 24.46708 23.97308 24.96108
predict(lm.fit, data.frame(horsepower=c(98)), interval="prediction")
#       fit     lwr      upr
#1 24.46708 14.8094 34.12476
```

(b) Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r}
plot(horsepower, mpg)
abline(lm.fit)
```

(c) Use the plot() function to produce diagnostic plots of the least
squares regression fit. Comment on any problems you see with
the fit.

```{r}
par(mfrow=c(2,2))
plot(lm.fit)
#Based on the residuals plots, there is some evidence of non-linearity.
```

13. In this exercise you will create some simulated data and will fit simple
linear regression models to it. Make sure to use set.seed(1) prior to
starting part (a) to ensure consistent results.
(a) Using the rnorm() function, create a vector, x, containing 100
observations drawn from a N(0, 1) distribution. This represents
a feature, X.

```{r}
set.seed(1)
x = rnorm(100)
```

(b) Using the rnorm() function, create a vector, eps, containing 100
observations drawn from a N(0, 0.25) distribution i.e. a normal
distribution with mean zero and variance 0.25.

```{r}
eps = rnorm(100, 0, sqrt(0.25))
```

(c) Using x and eps, generate a vector y according to the model
Y = −1 + 0.5X + e (3.39)
What is the length of the vector y? What are the values of β0
and β1 in this linear model?

```{r}
y = -1 + 0.5*x + eps
#y is of length 100. β0 is -1, β1 is 0.5.
```

(d) Create a scatterplot displaying the relationship between x and
y. Comment on what you observe.

```{r}
plot(x,y)
#I observe a linear relationship between x and y with a positive slope.
```

(e) Fit a least squares linear model to predict y using x. Comment
on the model obtained. How do ˆ β0 and ˆ β1 compare to β0 and
β1?

```{r}
lm.fit = lm(y~x)
summary(lm.fit)
#The linear regression fits a model close to the true value of the coefficients as was constructed. The model has a large F-statistic with a near-zero p-value so the null hypothesis can be rejected.
```

(f) Display the least squares line on the scatterplot obtained in (d).
Draw the population regression line on the plot, in a different
color.

```{r}
plot(x, y)
x<- plot(x,y)
abline(lm.fit, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
```

(h) Repeat (a)–(f) after modifying the data generation process in
such a way that there is less noise in the data. The model (3.39)
should remain the same. You can do this by decreasing the variance
of the normal distribution used to generate the error term
e in (b). Describe your results.

```{r}
set.seed(1)
eps1 = rnorm(100, 0, 0.125)
x1 = rnorm(100)
y1 = -1 + 0.5*x1 + eps1
plot(x1, y1)
x <- plot(x1, y1)
x
lm.fit1 = lm(y1~x1)
summary(lm.fit1)
abline(lm.fit1, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
#the error observed in R^2 and RSE decreases considerably.
```

(i) Repeat (a)–(f) after modifying the data generation process in
such a way that there is more noise in the data. The model
(3.39) should remain the same. You can do this by increasing
the variance of the normal distribution used to generate the
error term e in (b). Describe your results.

```{r}
set.seed(1)
eps2 = rnorm(100, 0, 0.5)
x2 = rnorm(100)
y2 = -1 + 0.5*x2 + eps2
plot(x2, y2)
lm.fit2 = lm(y2~x2)
summary(lm.fit2)
abline(lm.fit2, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
#the error observed in R^2 and RSE increases considerably.

```

(j) What are the confidence intervals for β0 and β1 based on the
original data set, the noisier data set, and the less noisy data
set? Comment on your results.

```{r}
confint(lm.fit)
confint(lm.fit1)
confint(lm.fit2)
#All intervals seem to be centered on approximately 0.5.
```

15. This problem involves the Boston data set, which we saw in the lab
for this chapter. We will now try to predict per capita crime rate
using the other variables in this data set. In other words, per capita
crime rate is the response, and the other variables are the predictors.
(a) For each predictor, fit a simple linear regression model to predict
the response. Describe your results. In which of the models is
there a statistically significant association between the predictor
and the response? Create some plots to back up your assertions.

```{r}
library(MASS)
summary(Boston)
Boston$chas <- factor(Boston$chas, labels = c("N","Y"))
summary(Boston)
attach(Boston)
lm.zn = lm(crim~zn)
summary(lm.zn) # yes
lm.indus = lm(crim~indus)
summary(lm.indus) # yes
lm.chas = lm(crim~chas) 
summary(lm.chas) # no
lm.nox = lm(crim~nox)
summary(lm.nox) # yes
lm.rm = lm(crim~rm)
summary(lm.rm) # yes
lm.age = lm(crim~age)
summary(lm.age) # yes
lm.dis = lm(crim~dis)
summary(lm.dis) # yes
lm.rad = lm(crim~rad)
summary(lm.rad) # yes
lm.tax = lm(crim~tax)
summary(lm.tax) # yes
lm.ptratio = lm(crim~ptratio)
summary(lm.ptratio) # yes
lm.black = lm(crim~black)
summary(lm.black) # yes
lm.lstat = lm(crim~lstat)
summary(lm.lstat) # yes
lm.medv = lm(crim~medv)
summary(lm.medv) # yes
#All, except chas. Plot each linear regression using "plot(lm)" to see residuals.
```

